\chapter{Available RPMs}
\label{apx:rpms}

The \cvmfs\ software is available in form of several RPM packages:
\begin{description}
	\item[cvmfs-release] Adds the \cvmfs\ yum repository.
	\item[cvmfs-config-default] Contains a configuration and public keys suitable \eg for nodes in the Worldwide LHC Computing Grid.  Provides access to repositories in the cern.ch, egi.eu, and opensciencegrid.org domains.
	\item[cvmfs-config-none] Empty package to satisfy the cvmfs-config requirement of the cvmfs package without actually installing any configuration.
	\item[cvmfs] Contains the Fuse module and additional client tools.  It has dependencies to at least one of the cvmfs-config-$\cdots$ packages.
	\item[cvmfs-devel] Contains the \texttt{libcvmfs.a} static library and the \texttt{libcvmfs.h} header file for use of \cvmfs\ with Parrot\cite{parrot05}.
	\item[cvmfs-auto-setup] Only available through yum. 
		This is a wrapper for \texttt{cvmfs\_config setup}. 
		This is supposed to provide automatic configuration for the ATLAS Tier3s.
		Depends on cvmfs.
	\item[cvmfs-server] Contains the \cvmfs\ server tool kit for maintaining Stratum~0 and Stratum~1 servers.
	\item[kernel-$\cdots$-.aufs21] Scientific Linux 6 kernel with aufs.
		Required for SL6 based Stratum~0 servers.
	\item[kernel-$\cdots$-.aufs3] Scientific Linux 7 kernel with aufs.
		Required for SL7/CC7 based Stratum~0 servers.
	\item[cvmfs-unittests] Contains the \texttt{cvmfs\_unittests} binary.  Only required for testing.
\end{description}
