\begin{longtable}{lX}
	\toprule
	{\bf\centering File Path} & {\bf\centering Description} \\
	\midrule

	\texttt{/srv/cvmfs} & \textbf{Central repository storage location} \newline
	Can be mounted or symlinked to another location \emph{before} creating the first repository. \\
	\addlinespace

	\texttt{/srv/cvmfs/<fqrn>} & \textbf{Storage location of a specific repository} \newline
	Can be symlinked to another location \emph{before} creating the repository \texttt{<fqrn>}. This location needs to be both writable by the repository owner and accessible through an HTTP server. \\
	\addlinespace

	\texttt{/srv/cvmfs/<fqrn>/.cvmfspublished} & \textbf{Manifest file of the repository} \newline
	The manifest provides the entry point into the repository. It is the only file that needs to be signed by the repository's private key. \\
	\addlinespace

	\texttt{/srv/cvmfs/<fqrn>/.cvmfswhitelist} & \textbf{List of trusted repository certificates} \newline
	Contains a list of certificate fingerprints that should be allowed to sign a repository manifest (see .cvmfspublished). The whitelist needs to be signed by a globally trusted private key.\\
	\addlinespace

	\texttt{/srv/cvmfs/<fqrn>/data} & \textbf{CAS location of the repository} \newline
    Data storage of the repository. Contains catalogs, files, file chunks, certificates and history databases in a content addressable file format. This directory and all its contents need to be writable by the repository owner.\\
	\addlinespace

	\texttt{/srv/cvmfs/<fqrn>/data/00..ff} & \textbf{Second CAS level directories} \newline
	Splits the flat CAS namespace into multiple directories. First two digits of the file content hash defines the directory the remainder is used as file name inside the corresponding directory.\\
	\addlinespace

	\texttt{/srv/cvmfs/<fqrn>/data/txn} & \textbf{CAS transaction directory} \newline
	Stores partial files during creation. Once writing has completed, the file is committed into the CAS using an atomic rename operation. \\
	\addlinespace

	\bottomrule
	\caption{Constituents of a local \cvmfs\ data backend storage location.}
	\label{tbl:localbackendanatomy}
\end{longtable}
