\begin{longtable}{lX}
	\toprule
	{\bf\centering File Path} & {\bf\centering Description} \\
	\midrule

	\texttt{/var/spool/cvmfs} & \textbf{\cvmfs\ server spool area} \newline
	Contains administrative and scratch space for \cvmfs\ repositories. This directory should only contain directories corresponding to individual \cvmfs\ repositories. \\
	\addlinespace

	\texttt{/var/spool/cvmfs/<fqrn>} & \textbf{Individual repository spool area} \newline
	Contains the spool area of an individual repository and might temporarily contain large data volumes during massive repository updates. This location can be mounted or symlinked to other locations. Furthermore it must be writable by the repository owner. \\
	\addlinespace

	\texttt{/var/spool/cvmfs/<fqrn>/cache} & \textbf{\cvmfs\ client cache directory} \newline
	Contains the cache of the \cvmfs\ client mounting the r/o branch (i.e. \texttt{/var/spool/cvmfs/<fqrn>/rdonly}) of the \aufs\ mount point located at \texttt{/cvmfs/<fqrn>}. The content of this directory is fully managed by the \cvmfs\ client and hence must be configured as a \cvmfs\ cache and writable for the repository owner. \\
	\addlinespace

	\texttt{/var/spool/cvmfs/<fqrn>/rdonly} & \textbf{\cvmfs\ client mount point} \newline
	Serves as the mount point of the \cvmfs\ client exposing the latest published state of the \cvmfs\ repository. It needs to be owned by the repository owner and should be empty if \cvmfs\ is not mounted to it. \\
	\addlinespace

	\texttt{/var/spool/cvmfs/<fqrn>/scratch} & \textbf{Writable \aufs\ scratch area} \newline
	All file system changes applied to \texttt{/cvmfs/<fqrn>} during a transaction will be stored in this directory. Hence, it potentially needs to accommodate a large data volume during massive repository updates. Furthermore it needs to be writable by the repository owner. \\
	\addlinespace

	\texttt{/var/spool/cvmfs/<fqrn>/tmp} & \textbf{Temporary scratch location} \newline
	Some \cvmfs\ server operations like publishing store temporary data files here, hence it needs to be writable by the repository owner. If the repository is idle this directory should be empty.  \\
	\addlinespace

	\texttt{/var/spool/cvmfs/<fqrn>/client.config} & \textbf{\cvmfs\ client configuration} \newline
	This contains client configuration variables for the \cvmfs\ client mounted to \texttt{/var/spool/cvmfs/<fqrn>/rdonly}. Most notibly it needs to contain \texttt{CVMFS\_ROOT\_HASH} configured to the latest revision published in the corresponding repository. This file needs to be writable by the repository owner. \\
	\addlinespace

	\bottomrule
	\caption{Constituents of the repository spool area.}
	\label{tbl:repospoolanatomy}
\end{longtable}